\section{Glossary}
	\subsection*{C}
	\addcontentsline{toc}{subsection}{C}
		\subsubsection*{Cubit}
		Cubit is the custom Ethereum currency of \textit{Soldino}, it has the value 
		of 1\euro. All prices shown are in Cubits. The Government can mint 
		and distribute Cubits to the platform's users.
		\subsubsection*{CC}
		Short version of Cubit, see Cubit above.
	
	\subsection*{D}
	\addcontentsline{toc}{subsection}{D}
		\subsubsection*{Deferred payment}
		Businesses can choose to not pay their due taxes immediately and pay it 
		later.
		\subsubsection*{Digital wallet}
		Digital wallets are where virtual currency is stored.
	
	\subsection*{E}
	\addcontentsline{toc}{subsection}{E}
		\subsubsection*{Ether}
		Ether is the currency of Ethereum.
		\subsubsection*{Ethereum}
		Ethereum is an open software platform based on blockchain technology 
		that enables developers to build and deploy decentralized applications.
		
	\subsection*{G}
	\addcontentsline{toc}{subsection}{G}
		\subsubsection*{Gas}
		Gas is the cost of transactions made on the Etehreum network. It is 
		measured in GWEI which is a billionth of an Ether.
		
	\subsection*{M}
	\addcontentsline{toc}{subsection}{M}
		\subsubsection*{MetaMask}
		MetaMask is a Plug-in available for Chrome, Firefix, Opera and Brave that 
		allows you to interact with the Ethereum network without hosting a node 
		and create multiple digital wallets\glo.
		\\It is required to use in \textit{Soldino}.
		
	\subsection*{P}
		\addcontentsline{toc}{subsection}{E}
		\subsubsection*{Product}
		Products include both goods and services.
		
	\subsection*{V}
	\addcontentsline{toc}{subsection}{V}
		\subsubsection*{VAT}
		VAT or value-added tax is a type of tax that is assessed incrementally, 
		based on the increase in value of a product or service. The VAT 
		percentage is chosen by the product's seller.