\section{Introduction} 
\subsection{Manual contents}
This document is the developer manual of he project \textit{Soldino}, developed by the team \textit{8Lab Solutions} for the proponent \textit{Red Babel}.\newline
Within the manual you can find:
\begin{itemize}
	\item the technologies used for the development;
	\item the software tools used and suggested;
	\item the software architecture;
	\item the architectural and design pattern used;
	\item the functionalities provided by \textit{Soldino}.
\end{itemize}

\subsection{Purpose of the manual}
The contents of the manual are intended to help the developers who decide to further develop or maintain \textit{Soldino}. Everything described here can help the developer to fully and deeply understand the design, use and features of the application, so that it can be modified and improved with ease.\newline
Many technologies, tools and languages are used to build the app: these are only briefly explained in their parts that cover the application domain. Additional references can be found in the "Reference" section.

\subsection{Purpose of the product}
%Lo scopo del prodotto è lo sviluppo di una ÐApp G accessibile attraverso interfaccia web con
%l’ausilio del plug-in G MetaMask G , che offra le funzionalità di piattaforma per la compravendita
%di beni e/o servizi, gestita dal governo G . L’interfaccia web verrà sviluppata con React G e Redux G ,
%mentre il back end G sarà gestito da un set di smart contracts G scritti utilizzando il linguaggio
%Solidity G , che verranno eseguiti su una rete Ethereum G . Il mezzo di pagamento sarà un token G
%basato sullo standard ECR20 G , denominato Cubit G e gestito dal governo G .
The platform \textit{Soldino} is a DApp accessible on a web browser as a client interface and the plugin Metamask as a virtual wallet.\newline
The main functionality of \textit{Soldino} is trading goods and services online. Since the platform's backend is coded on the Ethereum blockchain, it provides more security and transparency than the traditional e-commerce websites.\newline
The platform is built to be managed by the government. The currency used in it is called Cubit, and it's a ERC20 compliant fork of Ether, minted and managed by the government itself.


\subsection{Glossary}

\subsection{References}

\subsubsection{Normative}
\begin{itemize}
	\item \textbf{none}
\end{itemize}

\subsubsection{Informative}
\begin{itemize}
	\item \textbf{none}
\end{itemize}