\section{Setup} 
\subsection{Requirements}
In this section we describe all the requirements needed.
\subsubsection{Browser}
Soldino is accessible through a web interface. The currently most recent versions of the following broswers are supported:
\begin{itemize}
	\item \textbf{Mozilla Firefox}: version 66.0.1;
	\item \textbf{Google Chrome} version 73.0.3683.86.
\end{itemize}

\subsubsection{Tools}
The following tools are needed:
\begin{itemize}
	\item \textbf{Node.js}: you need it to run commands and as a Truffle requirement;
	\item \textbf{Truffle}: you need it to write and deploy contracts with ease;
	\item \textbf{Ganache}: you need it to put up a local Ethereum network and check transactions on it;
	\item \textbf{Metamask}: a browser plugin used as a virtual wallet.
	\item \textbf{Surge.sh}: the web platform chosen to host the website interface of Soldino.
\end{itemize}

\subsubsection{Dependencies}
Soldino depends on many different packages, some for use and others for development.\\
All these packages are located in the file \texttt{package.json} which is in the root folder of the project.\\
The packages required to execute the software \textit{Soldino} are listed below.\\

\renewcommand{\arraystretch}{1.5}
\rowcolors{2}{pari}{dispari}
\begin{longtable}{ 
		>{\centering}p{0.4\textwidth} 
		>{\centering}p{0.4\textwidth}
	}
	\caption{Packages required for software usage}\\
	\rowcolorhead
	\textbf{\color{white}Software} & 
	\textbf{\color{white}Version}
	\tabularnewline  
	\endhead	
	
	% voci prese da package.json, repo "Soldino-PoC, ramo "develop"


	react-text-mask & $\geq$5.4.4
	\tabularnewline
	commondir &$\geq$1.0.1
	\tabularnewline
	history &$\geq$4.7.2
	\tabularnewline
	prop-types &$\geq$15.7.2\tabularnewline
	react &$\geq$16.8.3\tabularnewline
	react-dom &$\geq$16.8.3\tabularnewline
	react-number-format &$\geq$4.0.6\tabularnewline
	react-redux &$\geq$6.0.1\tabularnewline
	react-router &$\geq$4.3.1\tabularnewline
	react-router-dom &$\geq$4.3.1\tabularnewline
	react-router-redux &$\geq$4.0.8\tabularnewline
	react-scripts &$\geq$2.1.8\tabularnewline
	redux &$\geq$4.0.1\tabularnewline
	redux-thunk &$\geq$2.3.0\tabularnewline
	web3 & 1.0.0-beta.37\tabularnewline
	
\end{longtable}

Other packages, listed below, are required for the development.
\renewcommand{\arraystretch}{1.5}
\rowcolors{2}{pari}{dispari}
\begin{longtable}{ 
		>{\centering}p{0.4\textwidth} 
		>{\centering}p{0.4\textwidth}
	}
	\caption{Packages required for development}\\
	\rowcolorhead
	\textbf{\color{white}Software} & 
	\textbf{\color{white}Version}
	\tabularnewline  
	\endhead	
	
	% voci prese da package.json, repo "Soldino-PoC, ramo "develop"
	eslint & 5.12.0\tabularnewline
	eslint-config-airbnb &$\geq$17.1.0\tabularnewline
	eslint-loader & $\geq$2.1.2\tabularnewline
	eslint-plugin-import & $\geq$2.16.0\tabularnewline
	eslint-plugin-jsx-a11y & $\geq$6.2.1\tabularnewline
	pre-commit & $\geq$1.2.2\tabularnewline
	truffle-contract & $\geq$4.0.6
	
\end{longtable}

\subsection{Installing}
\subsubsection{Browser}
The first thing is to have your browser installed. You can get the latest chrome version  \href{https://www.google.com/chrome/}{here}.\\

\subsubsection{Node}
Install Node.js. Digit on the shell the following commands:
\begin{enumerate}
	\item \texttt{curl -sL https://deb.nodesource.com/setup\_11.x | sudo -E bash -}
	\item \texttt{sudo apt-get install -y nodejs}
	\item check that \texttt{node} have been installed correctly with \texttt{node -v}.
\end{enumerate}
There is no need to install npm separately, since it is automatically installed with Node.

\subsubsection{Truffle}
Third thing: install Truffle.\\
Truffle requirements are:
\begin{itemize}
	\item an OS among Linux, Windows and MacOS (prefer Linux);
	\item NodeJS v8.9.4 or later (we picked version 11);
	\item Node Package Manager (npm).
\end{itemize}
You can then install Truffle with the command:
\begin{itemize}
	\item[] \texttt{npm install -g truffle}
\end{itemize}

\subsubsection{Ganache}
Fourth step: installing Ganache. There are three step to install Ganache:
\begin{enumerate}
	\item you can download the Ganache executable at this \href{https://truffleframework.com/ganache}{link}, clicking on the download button.;
	\item give the permissions to make the Ganache file executable. This can be done on Linux with the command \texttt{chmod +x path-of-the-appimage/ganache-1.3.0-x86\_64.AppImage};
	\item eventually, run it double clicking on the icon.
\end{enumerate}

\subsection{MetaMask}
MetaMask comes in the form of browser extension. You can add it to your browser this way:
\begin{itemize}
	\item Chrome:  \href{https://chrome.google.com/webstore/search/metamask?hl=it}{https://chrome.google.com/webstore/search/metamask?hl=it};
	\item Firefox: \href{https://addons.mozilla.org/it/firefox/addon/ether-metamask/?src=search}{https://addons.mozilla.org/it/firefox/addon/ether-metamask/?src=search}.
\end{itemize}

\subsection{Surge}
Install Surge.sh with the shell command
\begin{itemize}
	\item[]\texttt{npm install -g surge}.
\end{itemize}


\subsection{Configuration}
This section shows how to properly configure your work environment, so that it's the same as the one we worked on. 
This way you will hopefully encounter as little troubles as possible.\\


\subsection{Running}
Now that you have all the required software installed, it's time to get it up running.\\


\subsection{Deploying}
%not sure about this
This part shows how to deploy you contracts with Truffle and have them up running on Soldino.
