\section{Set up the work environment}
This chapter has the purpose to configure work environment like ours environment, of every members of 8Lab Solutions. \\
\textbf{Note}: if you are not contributing to this project but you are only using it, it
is not necessary to follow this section of the document.
\subsection{VS Code}
We use Microsoft VS Code for writing smart contracts, for react, redux and for testing our DApp. You can download Microsoft VS Code at the following link: \url{https://code.visualstudio.com/}. We use this environment because it offers useful plugins for Solidity and linting.
\subsection{ESLint plugin}
Useful plugin for VS Code that provide to linting file on typing. The extension uses the ESLint library installed in the open workspace folder.
It can be installed from the internal store of the program (accessible with Ctrl+Shift+X),
searching ”EsLint”.
\subsection{Solidity plugin}
VS Code has a useful plugin to check Solidity syntax and lint, called ”Solidity”.
It can be installed from the internal store of the program (accessible with Ctrl+Shift+X),
searching ”JuanBlanco Solidity”.
For further info about the installation and the configuration please visit the offi-
cial guide on GitHub, accessible from the following link:
https://github.com/
juanfranblanco/vscode-solidity
\subsection{React browser plugin}
To better debug React components it is recommended to use the following plugins: \\ \\
For Mozilla Firefox:
\url{https://addons.mozilla.org/it/firefox/addon/react-devtools} \\ \\
For Google Chrome:
\url{https://chrome.google.com/webstore/detail/react-developer-tools/fmkadmapgofadopljbjfkapdkoienihi}
\subsection{Redux browser plugin}
For checking Redux store and other Redux features it is recommended to use the following plugins: \\ \\
For Mozilla Firefox:
\url{https://addons.mozilla.org/it/firefox/addon/reduxdevtools/} \\ \\
For Google Chrome: \\
\url{https://chrome.google.com/webstore/detail/redux-devtools/lmhkpmbekcpmknklioeibfkpmmfibljd?hl=it}
