\section{Introduction} 
This document is the user manual of \textit{Soldino}, a project developed by 
	\textit{8Lab Solutions} based on Ethereum infrastructure. 
	\subsection{What is \textit{Soldino}}
	\textit{Soldino} is a platform, available on the following link \url{http://soldino.surge.sh/}, 
	that allows users to buy goods and services, allows companies to manage the 
	VATs related to those products and allows the Government to mint and 
	distribute Cubits\glo, refund companies of their VAT credit and manage 
	registered users.\\
	In particular:
	\begin{itemize}
		\item citizens can:
		\begin{itemize}
			\item  buy goods and services;
		\end{itemize}
		\item companies can:
		\begin{itemize}
			\item sell goods and services;
			\item buy goods and services;
			\item manage VAT;
		\end{itemize}
		\item Government can:
		\begin{itemize}
			\item mint Cubits\glo;
			\item distribute Cubits\glo;
			\item activate disabled users;
			\item deactivate active users;
			\item refund companies of their VAT credit;
		\end{itemize}
	\end{itemize}
	\textit{Soldino} is powered by the Ethereum\glosp network, allowing a high
	degree of security due to the distributed nature of the network.
	\subsection{Glossary}
	At the end of this document there is the appendix A where you can find 
	the definitions of terms that may be ambiguous or new to the users of 
	\textit{Soldino}. These terms are marked with a subscript \textit{G} 
	(e.g. example\glo).
	\subsection{Requirements}
	Please read carefully this section as it lists the requirements for 
	\textit{Soldino}
	 	\subsubsection{Browser}
		You must have one the following web browsers installed:
		\begin{itemize}
			\item Google Chrome version 71 or newer;
			\item Mozilla Firefox version 64 or newer.
		\end{itemize}
		\subsubsection{JavaScript}
		You must have JavaScript\glosp enabled. As a default option it is enabled but 
		,if you have it disabled, follow the following steps.\\
		For Google Chrome:
		\begin{enumerate}
			\item at the top right, click the three dots then "Settings";
			\item at the bottom, click "Advanced";
			\item under "Privacy and security" click "Content settings";
			\item click "JavaScript";
			\item turn on "Allowed (recommended)";
			\item refresh your browser.
		\end{enumerate}
		For Mozilla Firefox:
		\begin{enumerate}
			\item open a new window or tab;
			\item paste "about:config" in the address bar then press the Enter 
			key;
			\item on the following page, click the button: "I'll be careful, 
			I promise!";
			\item find the "javascript.enabled" row under the Preference Name 
			heading;
			\item double-click anywhere within the "javascript.enabled" row to 
			toggle the value from "False" to "True";
			\item refresh your browser.
		\end{enumerate}
		\subsubsection{MetaMask}
		You must install MetaMask\glosp plug-in in your browser. More 
		details will follow in the next section. 